sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-02 doc/paper-jss/paper-jss.Rmd
Preping JSS

---
documentclass: jss
author:
  - name: FirstName LastName
    orcid: 0000-0000-0000-0000
    affiliation: University/Company
    # use this syntax to add text on several lines
    address: |
      | First line
      | Second line
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Second Author
    orcid: 0000-0000-0000-0000
    affiliation: 'Affiliation \AND'
    # To add another line, use \AND at the end of the previous one as above
  - name: Third Author
    orcid: 0000-0000-0000-0000
    address: |
      | Department of Statistics and Mathematics,
      | Faculty of Biosciences,
      | Universitat Autònoma de Barcelona
    affiliation: |
      | Universitat Autònoma
      | de Barcelona
    # use a different affiliation in adress field (differently formated here)
    affiliation2: Universitat Autònoma de Barcelona
bibliography: refs.bib
title:
  formatted: "\\pkg{sdmTMB}: An \\proglang{R} Package for Fast, Flexible, and Accessible Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields"
  # If you use tex in the formatted title, also supply version without
  plain:     "sdmTMB: An R Package for Fast, Flexible, and Accessible Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields"
  # For running headers, if needed
  short:     "\\pkg{sdmTMB}: geostatistical SPDE-based GLMMs with \\pkg{TMB}"
abstract: >
  Geostatistical data are common across disciplines and available in increasingly large volumes. However, appropriate models to analyse these data, such as generalised linear mixed effects models (GLMMs) with Gaussian random fields, are computationally intensive and challenging to implement such that spatial autocorrelation is frequently ignored, or addressed in less interpretable ways. Here, we introduce the \proglang{R} package \pkg{sdmTMB}, which extends the flexible interface familiar to users of `stats::glm()`, \pkg{lme4}, \pkg{glmmTMB}, or \pkg{mgcv} to include spatial and spatiotemporal latent fields using a predictive-process SPDE-(stochastic partial differential equation) based approach. SPDE matrices are constructed with \pkg{INLA} and estimation is conducted via maximum marginal likelihood with Template Model Builder (\pkg{TMB}), although penalised likelihood and Bayesian inference (via \pkg{tmbstan} and \pkg{rstan}) are also possible. We describe the statistical model, illustrate the package through two case studies, and compare the functionality, speed, and interface to related software. The case studies illustrate \pkg{sdmTMB}'s flexibility and useability by implementing penalised smoothers, non-stationary processes (time-varying and spatially varying coefficients), and anisotropy (asymmetry in spatial correlations). Modelling of these common but computationally complex relationships is further aided by built-in handling of delta (hurdle) models, break-point effects, and diagnostic tools including out-of-sample cross validation. Finally, we demonstrate that \pkg{sdmTMB} is 4--16 times faster than \pkg{INLA} or \pkg{inlabru}. \pkg{sdmTMB}'s accessible interface has already opened this useful class of models to a wider audience within ecological species distribution modelling. We anticipate its application to the full spectrum geostatistical data will prove equally fruitful.
keywords:
  # at least one keyword must be supplied
  formatted: [test]
  plain:     [test]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{bm}
  \usepackage{lscape}
  \usepackage{tablefootnote}
  \usepackage{threeparttable}
  \usepackage{booktabs}
output: rticles::jss_article
---

@@

\begin{landscape}
\begin{figure}[p]
{\centering \includegraphics[width=9in]{../../figs/diagram}}
\caption[]{
Components of an \pkg{sdmTMB} model with illustrations, descriptions, examples, notation, and example code.
An \pkg{sdmTMB} model can be built from any combination of the process components (first six rows) plus an observation component (last row).
The examples are from an SDM context, but the model can be fit to any spatially referenced point data.
Notation:
We refer to design matrices as $\bm{X}$.
The indexes $\bm{s}$, $t$, and $g$ index spatial coordinates, time, and group, respectively.
The $\sigma$ and $\bm{\Sigma}$ symbols represent standard deviations and covariance matrices, respectively.
All other symbols refer to the  described model components (e.g., $\bm{\beta}$ and $\bm{\omega}$ refer to a vector of main effects and spatial random field deviations, respectively).
See Appendix 1 for a full description of the model.
Note that \texttt{s()} denotes a smoother as in \pkg{mgcv} [@wood2017a], \texttt{breakpt()} denotes a breakpoint 'hockey-stick' shape \citep[e.g.][]{barrowman2000}, \texttt{(1|g)} denotes a random intercept by group \texttt{g}, and \texttt{~ 0} is used in an \proglang{R} formula to omit an intercept.}\label{fig:diagram}
\end{figure}
\end{landscape}

@@

And we can run some basic checks on our model with the `sanity()` function:

```{r pcod-eg1-sanity}
sanity(fit)
```

@@

\begin{figure}
{\centering \includegraphics[width=5.2in]{../../figs/pcod-fig}}
\caption[]{Output from the Pacific cod spatial model example in Queen Charlotte Sound, BC, Canada. 
(A) SPDE mesh (lines) combined with the trawl survey observations (points). Finer meshes will be slower to fit but generally increase the accuracy of the SPDE approximation. The circle area corresponds to biomass density of Pacific cod caught on individual trawls. 
(B) Spatial random field: these values are shown in link (log) space and represent spatially correlated deviations that are not accounted for by the depth effect. (C) Overall prediction: these estimates represent the combination of all fixed and random effects. Crosses illustrate center of gravity (\texttt{get\_cog()}) from a spatiotemporal version; lighter crosses are more recent.
(D) Conditional effect of depth modelled as a penalized smoother. 
These predictions are made omitting the spatial random field.
(E) Standardized area-weighted population index derived from a spatiotemporal version (\texttt{get\_index()}). The line represents the estimate and the ribbon indicates a 95\% confidence interval ($\pm$ 2 SEs).}\label{fig:pcod-fig}
\end{figure}

We could extend this spatial model to be a spatiotemporal one simply by supplying the year column name to the `time` argument and specifying how we want the spatiotemporal random fields to be structured.
Here we will keep the spatial field and structure the spatiotemporal random fields as AR(1).

@@

```{r fit-tv, eval=TRUE, echo=TRUE, cache=TRUE, results='hide'}
fit_spatiotemporal <- sdmTMB(
  density ~ 0 + s(depth, k = 5), 
  time_varying = ~ 1,
  family = tweedie(link = "log"), 
  data = pcod,
  mesh = mesh,
  time = "year",
  spatial = "on",
  spatiotemporal = "iid",
  time_varying_type = "ar1",
  anisotropy = TRUE,
  silent = FALSE # print fitting progress
)
```

@@

This model took approximately `r round(as.numeric(t2 - t1), 0)` seconds to fit on our laptop. 
We can inspect the anisotropy with `plot_anisotropy()`, which plots an ellipse showing the spatial range with the spatial coordinates centered on zero.
We could generate an area-weighted population index (e.g., a relative or absolute index of abundance or biomass) that is independent of sampling locations by predicting from that fit on a grid covering the area of interest and summing the predicted biomass with the `get_index()` function (Fig.\ \ref{fig:pcod-fig}E, Appendix 2).

@@

\begin{figure}
{\centering \includegraphics[width=3.5in]{../../figs/timing-spatial-m1-april11}}
\caption[]{Comparison of time to fit an SPDE spatial random field model with 1000 observations, an intercept and one predictor, Gaussian error, and a sequence of SPDE resolutions. Lines represent means and ribbons 95% quantiles across 50 random iterations. Note the log x and y axes. \pkg{VAST} is similar to \pkg{sdmTMB} and so is not shown. \pkg{inlabru} used the empirical Bayes integration strategy and Gaussian approximation with `bru_max_iter = 1`, and the `like()` formulation. \pkg{mgcv} used \texttt{bam()}, \texttt{method = 'fREML'}, and discretized covariates [@miller2019]. Note that spaMM only fits spatial, not spatiotemporal, models.
All platforms were restricted to one core and could be faster with parallel computation or optimized algebra libraries.}\label{fig:timing}
\end{figure}

@@

>>>>

---
documentclass: jss
author:
  - name: Sean C. Anderson
    orcid: 0000-0001-9563-1937
    affiliation: 'Pacific Biological Station, Fisheries and Oceans Canada \AND'
    address: |
      | Pacific Biological Station, Nanaimo, BC, Canada
    email: \email{sean.anderson@dfo-mpo.gc.ca}
  - name: Eric J. Ward
    orcid: 0000-0002-4359-0296
    affiliation: 'Northwest Fisheries Science Center, National Marine Fisheries Service \AND'
  - name: Philina A. English
    orcid: 0000-0003-2992-6782
    address: ''
    affiliation: 'Pacific Biological Station, Fisheries and Oceans Canada \AND'
  - name: Lewis A. K. Barnett
    orcid: 0000-0002-9381-8375
    affiliation: 'Alaska Fisheries Science Center, National Marine Fisheries Service'
bibliography: refs.bib
title:
  formatted: "\\pkg{sdmTMB}: An \\proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields"
  # If you use tex in the formatted title, also supply version without
  plain:     "sdmTMB: An R Package for Fast, Flexible, and Accessible Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields"
  # For running headers, if needed
  short:     "\\pkg{sdmTMB}: geostatistical SPDE-based GLMMs with \\pkg{TMB}"
abstract: >
  Geostatistical data are common across disciplines and available in increasingly large volumes. However, appropriate models to analyse these data, such as generalised linear mixed effects models (GLMMs) with Gaussian random fields, are computationally intensive and challenging to implement such that spatial autocorrelation is frequently ignored, or addressed in less interpretable ways. Here, we introduce the \proglang{R} package \pkg{sdmTMB}, which extends the flexible interface familiar to users of `stats::glm()`, \pkg{lme4}, \pkg{glmmTMB}, or \pkg{mgcv} to include spatial and spatiotemporal latent fields using a predictive-process SPDE-(stochastic partial differential equation) based approach. SPDE matrices are constructed with \pkg{INLA} and estimation is conducted via maximum marginal likelihood with Template Model Builder (\pkg{TMB}), although penalised likelihood and Bayesian inference (via \pkg{tmbstan} and \pkg{rstan}) are also possible. We describe the statistical model, illustrate the package through two case studies, and compare the functionality, speed, and interface to related software. The case studies illustrate \pkg{sdmTMB}'s flexibility and useability by implementing penalised smoothers, non-stationary processes (time-varying and spatially varying coefficients), and anisotropy (asymmetry in spatial correlations). Modelling of these common but computationally complex relationships is further aided by built-in handling of delta (hurdle) models, break-point effects, and diagnostic tools including out-of-sample cross validation. Finally, we demonstrate that \pkg{sdmTMB} is 4--16 times faster than \pkg{INLA} or \pkg{inlabru}. \pkg{sdmTMB}'s accessible interface has already opened this useful class of models to a wider audience within ecological species distribution modelling. We anticipate its application to the full spectrum geostatistical data will prove equally fruitful.
keywords:
  # at least one keyword must be supplied
  formatted: [test]
  plain:     [test]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{bm}
  \usepackage{lscape}
  \usepackage{tablefootnote}
  \usepackage{threeparttable}
  \usepackage{booktabs}
output: rticles::jss_article
---

@@

\begin{landscape}
\begin{figure}[p]
\centering 
\includegraphics[width=9in]{../../figs/diagram}
\caption[]{
Components of an \pkg{sdmTMB} model with illustrations, descriptions, examples, notation, and example code.
An \pkg{sdmTMB} model can be built from any combination of the process components (first six rows) plus an observation component (last row).
The examples are from an SDM context, but the model can be fit to any spatially referenced point data.
Notation:
We refer to design matrices as $\bm{X}$.
The indexes $\bm{s}$, $t$, and $g$ index spatial coordinates, time, and group, respectively.
The $\sigma$ and $\bm{\Sigma}$ symbols represent standard deviations and covariance matrices, respectively.
All other symbols refer to the  described model components (e.g., $\bm{\beta}$ and $\bm{\omega}$ refer to a vector of main effects and spatial random field deviations, respectively).
See Appendix 1 for a full description of the model.
Note that \texttt{s()} denotes a smoother as in \pkg{mgcv} [@wood2017a], \texttt{breakpt()} denotes a breakpoint 'hockey-stick' shape \citep[e.g.][]{barrowman2000}, \texttt{(1|g)} denotes a random intercept by group \texttt{g}, and \texttt{~ 0} is used in an \proglang{R} formula to omit an intercept.}\label{fig:diagram}
\end{figure}
\end{landscape}

@@

We can run some basic checks on our model with the `sanity()` function:

```{r pcod-eg1-sanity, eval=TRUE, echo=TRUE}
sanity(fit)
```

```
#> Non-linear minimizer suggests successful convergence
#> Hessian matrix is positive definite
#> No extreme or very small eigen values detected
#> No gradients with respect to fixed effects are >= 0.001
#> No fixed-effect standard errors are NA
#> No fixed-effect standard errors look unreasonably large
#> No sigma parameters are < 0.01
#> No sigma parameters are > 100
#> Range parameter doesn't look unreasonably large
```

@@

\begin{figure}
\centering
\includegraphics[width=5.2in]{../../figs/pcod-fig}
\caption[]{Output from the Pacific cod spatial model example in Queen Charlotte Sound, BC, Canada. 
(A) SPDE mesh (lines) combined with the trawl survey observations (points). Finer meshes will be slower to fit but generally increase the accuracy of the SPDE approximation. The circle area corresponds to biomass density of Pacific cod caught on individual trawls. 
(B) Spatial random field: these values are shown in link (log) space and represent spatially correlated deviations that are not accounted for by the depth effect. (C) Overall prediction: these estimates represent the combination of all fixed and random effects. Crosses illustrate center of gravity (\texttt{get\_cog()}) from a spatiotemporal version; lighter crosses are more recent.
(D) Conditional effect of depth modelled as a penalized smoother. 
These predictions are made omitting the spatial random field.
(E) Standardized area-weighted population index derived from a spatiotemporal version (\texttt{get\_index()}). The line represents the estimate and the ribbon indicates a 95\% confidence interval ($\pm$ 2 SEs).}\label{fig:pcod-fig}
\end{figure}

We could extend this spatial model to be a spatiotemporal one simply by supplying the year column name to the `time` argument (`time = "year"`) and specifying how we want the spatiotemporal random fields to be structured.
Here we will keep the spatial field (`spatial = "on"`), structure the spatiotemporal random fields as independent (`spatiotemporal = "iid"`), include a time-varying intercept (`~ 1`) fit as an AR(1) process (`time_varying_type = "ar1"`), include anisotropy to allow spatial correlation to decay at different rates up the coast vs.\ away from the coast (`anisotropy = TRUE`), and use `silent = FALSE` to see model fitting progress.

@@

```{r fit-tv, eval=TRUE, echo=TRUE, cache=TRUE, results='hide'}
fit_spatiotemporal <- sdmTMB(
  density ~ 0 + s(depth, k = 5), 
  time_varying = ~ 1,
  family = tweedie(link = "log"), 
  data = pcod,
  mesh = mesh,
  time = "year",
  spatial = "on",
  spatiotemporal = "iid",
  time_varying_type = "ar1",
  anisotropy = TRUE,
  silent = FALSE
)
```

@@

This model took approximately `r round(as.numeric(t2 - t1), 0)` seconds to fit on our laptop. 
We could inspect the anisotropy with `plot_anisotropy()`, which plots an ellipse showing the spatial range with the spatial coordinates centered on zero.
We could generate an area-weighted population index (e.g., a relative or absolute index of abundance or biomass) that is independent of sampling locations by predicting from that fit on a grid covering the area of interest and summing the predicted biomass with the `get_index()` function (Fig.\ \ref{fig:pcod-fig}E, Appendix 2).

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{../../figs/timing-spatial-m1-april11}
\caption[]{Comparison of time to fit an SPDE spatial random field model with 1000 observations, an intercept and one predictor, Gaussian error, and a sequence of SPDE resolutions. Lines represent means and ribbons 95% quantiles across 50 random iterations. Note the log x and y axes. \pkg{VAST} is similar to \pkg{sdmTMB} and so is not shown. \pkg{inlabru} used the empirical Bayes integration strategy and Gaussian approximation with `bru_max_iter = 1`, and the `like()` formulation. \pkg{mgcv} used \texttt{bam()}, \texttt{method = 'fREML'}, and discretized covariates [@miller2019]. Note that spaMM only fits spatial, not spatiotemporal, models.
All platforms were restricted to one core and could be faster with parallel computation or optimized algebra libraries.}\label{fig:timing}
\end{figure}

@@

\clearpage

\appendix

```{r child="model-description.Rmd", echo=FALSE, cache=FALSE, eval=TRUE}
```

```{r child="pcod.Rmd", echo=FALSE, cache=FALSE, eval=TRUE}
```

```{r child="owls.Rmd", echo=FALSE, cache=FALSE, eval=TRUE}
```

```{r child="inla-comparison.Rmd", echo=FALSE, cache=FALSE, eval=TRUE}
```

```{r child="timing.Rmd", echo=FALSE, cache=FALSE, eval=TRUE}
```

### 2022-11-02 doc/paper-jss/pcod.Rmd
Preping JSS

---
title: "Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
bibliography: refs.bib
csl: mee.csl
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
  \linenumbers
---

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.asp = 0.618,
  cache = TRUE,
  autodep = TRUE,
  cache.comments = FALSE
)
```

@@

First, we construct a mesh to approximate the spatial process, which is used in the SPDE calculations. The `make_mesh()` function accepts the data coordinates and the minimum allowed distance between vertices (`cutoff`) or approximate number of knots in the mesh (`n_knots`). Custom built meshes with `INLA` (including meshes with barriers limiting covariance across polygons) can also be passed in. See examples included in `?make_mesh`.

@@

```{r mesh, echo = TRUE, cache=FALSE}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)
```

```{r plot-mesh, cache=FALSE, fig.align='center', fig.asp=1, out.width="3in"}
plot(mesh)
```

Next we will fit a GLMM (generalized linear mixed effects model). For this example, we will include `0 + as.factor(year)` so that there is a factor predictor that represents the mean estimate for each time slice. Setting `silent = FALSE` would give us optimization details as the model fits but clutter the R Markdown output.

@@

```{r fit-pcod, warning=FALSE, message=FALSE}
fit <- sdmTMB(density ~ 0 + as.factor(year),
  data = pcod,
  time = "year", mesh = mesh, family = tweedie(link = "log")
)
```

@@

```{r print-fit}
print(fit)
```

@@

```{r tidy}
tidy(fit, conf.int = TRUE)
tidy(fit, effects = "ran_pars", conf.int = TRUE)
```

@@

```{r predict}
pred <- predict(fit)
```

@@

```{r sim-resids, out.width="4in", warning=FALSE, results='hide'}
set.seed(123)
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

```{r mcmc-resids, warning=FALSE, results='hide', cache=TRUE}
set.seed(123)
r <- residuals(fit,
  type = "mle-mcmc", 
  mcmc_iter = 400, mcmc_warmup = 300
)
```

@@

```{r sims}
pred_sims <- predict(fit, newdata = qcs_grid, nsim = 500)
dim(pred_sims)
```

@@

```{r sims-cv-plot}
qcs_grid$cv <- apply(pred_sims, 1, function(x) sd(exp(x)) / mean(exp(x)))
ggplot(qcs_grid, aes(X, Y, fill = cv)) +
  geom_raster() +
  facet_wrap(~year) +
  coord_fixed() +
  scale_fill_viridis_c(trans = "log10", option = "D")
```

We can calculate our standardized population index by predicting on our survey domain grid and setting `return_tmb_object = TRUE`. This returns the TMB objective function, which is required to pass the output to `get_index()`.

```{r index, fig.asp=0.45, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, 
  return_tmb_object = TRUE
)
ind <- get_index(pred2, area = qcs_grid$area, bias_correct = TRUE)

@@

The above example uses `bias_correct = TRUE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more details can be found in the [TMB documentation](https://github.com/kaskr/adcomp/wiki) or [@thorson2016bias]. Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements a generic bias correction algorithm that should correct for this, but takes more time and memory than skipping the bias correction.

# References

>>>>

# Example: spatiotemporal modelling of Pacific cod

```{r setup-pcod, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.asp = 0.618,
  cache = TRUE,
  autodep = TRUE,
  cache.comments = FALSE,
  echo = TRUE
)
```

@@

First, we construct a mesh to approximate the spatial process, which is used in the SPDE calculations. The `make_mesh()` function accepts the data coordinates and the minimum allowed distance between vertices (`cutoff`) or approximate number of knots in the mesh (`n_knots`). Custom built meshes with \pkg{INLA} (including meshes with barriers limiting covariance across polygons) can also be passed in. See examples included in `?make_mesh`.

@@

```{r mesh, echo = TRUE, cache=TRUE}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)
```

```{r plot-mesh, cache=TRUE, fig.align='center', fig.asp=1, out.width="3in", echo=TRUE}
plot(mesh)
```

Next we will fit a GLMM. For this example, we will include `0 + as.factor(year)` so that there is a factor predictor that represents the mean estimate for each time slice. Setting `silent = FALSE` would gives us optimization details as the model fits.

@@

```{r fit-pcod, warning=FALSE, message=FALSE, cache=TRUE, echo=TRUE, results='hide'}
fit <- sdmTMB(
  density ~ 0 + as.factor(year),
  data = pcod,
  time = "year", 
  mesh = mesh,
  family = tweedie(link = "log"),
  silent = FALSE
)
```

@@

```{r print-fit, echo=TRUE}
print(fit)
```

@@

```{r pcod-tidy, echo=TRUE}
tidy(fit, conf.int = TRUE)
tidy(fit, effects = "ran_pars", conf.int = TRUE)
```

@@

```{r pcod-predict, cache=TRUE, echo=TRUE}
pred <- predict(fit)
```

@@

```{r sim-resids, out.width="4in", warning=FALSE, results='hide', cache=TRUE, echo=TRUE}
set.seed(123)
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

```{r mcmc-resids, warning=FALSE, results='hide', cache=TRUE}
set.seed(123)
r <- residuals(fit,
  type = "mle-mcmc", 
  mcmc_iter = 200, mcmc_warmup = 100
)
```

@@

```{r pcod-sims, cache=TRUE}
pred_sims <- predict(fit, newdata = qcs_grid, nsim = 200)
dim(pred_sims)
```

@@

```{r sims-cv-plot, cache=TRUE}
qcs_grid$cv <- apply(pred_sims, 1, function(x) sd(exp(x)) / mean(exp(x)))
ggplot(qcs_grid, aes(X, Y, fill = cv)) +
  geom_raster() +
  facet_wrap(~year) +
  coord_fixed() +
  scale_fill_viridis_c(trans = "log10", option = "D")
```

We can calculate a standardized population index by predicting on our survey domain grid and setting `return_tmb_object = TRUE`. This returns the \pkg{TMB} objective function, which is required to pass the output to `get_index()`.

```{r pcod-app-index, fig.asp=0.45, out.width="5in", cache=TRUE}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, 
  return_tmb_object = TRUE
)
ind <- get_index(pred2, area = qcs_grid$area, bias_correct = TRUE)

@@

The above example uses `bias_correct = TRUE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more details can be found in @thorson2016bias. Leaving `bias_correct = FALSE` is fine for experimentation, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements a generic bias correction algorithm that should correct for this, but takes more time and memory than skipping the bias correction.
